Automated Program Verification and Synthesis of Embedded \& Cyber-Physical Systems: Advances and Challenges

### 2018-02-05 paper.tex
introduction to section 3
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

\begin{document}
%
% paper title
% Titles are generally capitalized except for words such as a, an, and, as,
% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
% not capitalized unless they are the first or last word of the title.
% Linebreaks \\ can be used within to get better formatting as desired.
% Do not put math or special symbols in the title.
\title{Automated Program Verification and Synthesis of Embedded \& Cyber-physical Systems: Advances and Challenges}

@@

%--------------------------------------
\subsection{Automated and Formal Verification of Cyber-physical systems}
\label{ssec:verification}
%--------------------------------------

@@

%--------------------------------------
\section{SAT-based and SMT-based Verification Techniques}
\label{Preliminaries}
%--------------------------------------

>>>>

\begin{document}
%
% paper title
% Titles are generally capitalized except for words such as a, an, and, as,
% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
% not capitalized unless they are the first or last word of the title.
% Linebreaks \\ can be used within to get better formatting as desired.
% Do not put math or special symbols in the title.
\title{Automated Program Verification and Synthesis of Embedded \& Cyber-Physical Systems: Advances and Challenges}

@@

%--------------------------------------
\subsection{Automated and Formal Verification of Cyber-Physical Systems}
\label{ssec:verification}
%--------------------------------------

@@

%--------------------------------------
\section{SAT- and SMT-based Verification and Synthesis Techniques}
\label{Preliminaries}
%--------------------------------------

%The amount of software embedded in CPS is increasing, partly due to increased design complexity, but also as a result of shift toward software-centric implementations, which designers prefer because software allows them to flexibly and efficiently implement new features. Synthesis is one of the key automation techniques for improving productivity and developing efficient implementations for a design specification.

\textcolor{blue}{Due to the advent of sophisticated SMT solvers built over efficient SAT solvers, an increasingly number of software verifiers and synthesizers are being developed in the literature, in order to improve  productivity and produce efficient implementations for a ECPS design specification. Here, we describe recent advances in symbolic model checking of software, including BMC, \textit{k}-induction, and Craig interpolation techniques. This section also overviews software synthesis techniques that also use logic to describe states and transformations between system states.}
